\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-29 paper/ms.tex
Add verbose Tc definition

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search\cite{2017AJ....153..257O} for comoving stars using the
proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
catalog (hereafter \tgas), a component of the first data release of the
astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(Table~\ref{tab:t1}).
The abundances are noted as \elemH{X}, defined as the log ratio of number
density of element \elem{X} to \elem{H} relative to the solar value
($\elemH{X} = \log_{10} ((n_X / n_H) / (n_X / n_H)_\odot)$).
Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
For lithium, we use the absolute abundance defined as $A(\elem{Li}) = 12 +
\log_{10} (n_\elem{Li}/n_\elem{H})$.

@@

Sorting the abundance differences by $50$\% condensation temperature ($T_C$) of the
elements shows a clear increasing trend.
In \figname~\ref{fig:deltaxh_tcrank},
we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
by each element's equilibrium \Tcondens\ in solar system composition
gas\cite{2003ApJ...591.1220L}.
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile of all elements measured.
The differences in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggest a break in $\Tcondens \approx 1200$~K.

>>>>

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search\cite{2017AJ....153..257O} for comoving stars using the
proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
catalog (hereafter \tgas), a component of the first data release of the
astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(Table~\ref{tab:t1}).
The abundances are noted as \elemH{X}, defined as the log ratio of number
density of element \elem{X} to \elem{H} relative to the solar value
($\elemH{X} = \log_{10} ((n_X / n_H) / (n_X / n_H)_\odot)$).
Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
For lithium, we also use the absolute abundance defined as $A(\elem{Li}) = 12 +
\log_{10} (n_\elem{Li}/n_\elem{H})$.

@@

Sorting the abundance differences by $50$\% condensation temperature ($T_C$) of the
elements, defined as the temperature at which $50$\% of the element in mass
is condensed into solid forms, shows a clear increasing trend.
In \figname~\ref{fig:deltaxh_tcrank},
we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
by each element's equilibrium \Tcondens\ in solar system composition
gas\cite{2003ApJ...591.1220L}.
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile of all elements measured.
The differences in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggest a break in $\Tcondens \approx 1200$~K.
